EDA

### 2020-03-01 src/EDA&mode_fitting.Rmd
delete highly correlated variable predTaxIncome in all models

linear_full<-lm(rate~.,data=assessment_aggregate)
summary(linear_full)

library(broom)
linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) #  2.772333

```
Multiple R-squared:  0.7803,	Adjusted R-squared:  0.7503 
MSPE = 2.772333

Next: variable selection
with only significant variables
```{r}
reduced<-lm(rate~Year+TaxClassCode+AddressAssessorMunicipalityDesc, data=assessment_aggregate)
summary(reduced)

reduced_fit<-augment(reduced)
sqrt(sum((reduced_fit$.resid)^2)/nrow(assessment_aggregate)) #  2.861619

```
Multiple R-squared:  0.7659,	Adjusted R-squared:  0.7408 
MSPE = 2.861619
With fewer variables, adjusted R-squared declines.

By comparing the two models, the fit of full model is better.

@@

Ridge Regression
reference: https://www.pluralsight.com/guides/linear-lasso-and-ridge-regression-with-r
```{r}
library(glmnet)
library(dummies)
dummy_year<-dummy(assessment_aggregate$Year)
dummy_municipal<-dummy(assessment_aggregate$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_aggregate$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_year,dummy_taxclass,assessment_aggregate$assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$predTaxIncome,assessment_aggregate$tax)

@@

```
MSPE = 1.992244
Rsquare=0.8865213

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
eval_results(y, predictions_train)
```
MSPE = 1.985639
Rsquare=0.8872724

Elastic net: 
reference: https://daviddalpiaz.github.io/r4sl/elastic-net.html
```{r}
library(caret)
tibble::as_tibble(assessment_aggregate)
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~., data = assessment_aggregate,
  method = "glmnet",
  trControl = cv_10
)
elastic_net
```
The final values used for the model were alpha = 0.1 and lambda = 0.09334029.
MSPE = 3.066083  
R squared = 0.7459584

Among these all the models, lasso seems to have the best goodness of fit.

@@

newx<-test[,-c(8)]
y<-test[,c(8)]
linear_1<-lm(rate ~.,data=train)
resid<-predict(linear_1,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE = 3.52065

Reduced model
```{r}
# reduced variable
linear_2<-lm(rate~Year+TaxClassCode+AddressAssessorMunicipalityDesc,data=train)
resid<-predict(linear_2,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
# 3.516749
```
MSPE = 3.516749

@@

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.530686

Ridge
```{r}
ridge_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0, family = 'gaussian', lambda = lambdas)
set.seed(450)
cv_ridge <- cv.glmnet(x_train, y_train, alpha = 0, lambda = lambdas, nfolds=10)
optimal_lambda <- cv_ridge$lambda.min
optimal_lambda
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.568047

Elastic Net
```{r}
tibble::as_tibble(assessment_aggregate[train_ind,])
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~., data = assessment_aggregate[train_ind,],
  method = "glmnet",
  trControl = cv_10
)
elastic_net
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were alpha = 0.55 and lambda = 0.009140377.

ridge_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0.55, family = 'gaussian', lambda = 0.009140377)
predictions_test <- predict(ridge_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.566096

>>>>

colnames(assessment_aggregate)
linear_full<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+tax,data=assessment_aggregate)
summary(linear_full)

library(broom)
linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) 
```
Multiple R-squared:  0.8874,	Adjusted R-squared:  0.8707 
MSPE =  1.984285

Next: variable selection
with only significant variables
```{r}
reduced<-lm(rate~factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+assessTotal+landTotal, data=assessment_aggregate)
summary(reduced)

reduced_fit<-augment(reduced)
sqrt(sum((reduced_fit$.resid)^2)/nrow(assessment_aggregate))
```
Multiple R-squared:  0.8874,	Adjusted R-squared:  0.8721 
MSPE = 1.984541

@@

Ridge Regression
reference: https://www.pluralsight.com/guides/linear-lasso-and-ridge-regression-with-r
```{r}
library(glmnet)
library(dummies)
dummy_year<-dummy(assessment_aggregate$Year)
dummy_municipal<-dummy(assessment_aggregate$AddressAssessorMunicipalityDesc)
dummy_taxclass<-dummy(assessment_aggregate$TaxClassCode)
# build x matrix
x<-cbind(dummy_municipal,dummy_year,dummy_taxclass,assessment_aggregate$assessTotal,assessment_aggregate$landTotal,assessment_aggregate$improvementTotal,assessment_aggregate$propertyCount,assessment_aggregate$tax)

@@

```
MSPE = 1.989583
Rsquare=	0.8868242

@@

predictions_train <- predict(lasso_model, s = lambda_best, newx = x)
eval_results(y, predictions_train)
```
MSPE = 1.985463	
Rsquare=0.8872924

Elastic net: 
reference: https://daviddalpiaz.github.io/r4sl/elastic-net.html
```{r}
library(caret)
tibble::as_tibble(assessment_aggregate)
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount, data = assessment_aggregate,
  method = "glmnet",
  trControl = cv_10
)
elastic_net
```
The final values used for the model were alpha = 0.1 and lambda = 0.007102922.
   alpha  lambda       RMSE      Rsquared   MAE     
  0.10   0.007102922  2.236598  0.8625398  1.708885

@@

newx<-test[,-c(8,9)]
y<-test[,c(8)]
linear_1<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+tax,data=train)
resid<-predict(linear_1,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE =  2.590233

Reduced model
```{r}
# reduced variable
linear_2<-lm(rate~factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc)+assessTotal+landTotal,data=train)
resid<-predict(linear_2,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE = 2.523658

@@

predictions_test <- predict(lasso_model, s = lambda_best, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.528047

Ridge
```{r}
ridge_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0, family = 'gaussian', lambda = lambdas)
set.seed(450)
cv_ridge <- cv.glmnet(x_train, y_train, alpha = 0, lambda = lambdas, nfolds=10)
optimal_lambda <- cv_ridge$lambda.min
optimal_lambda
predictions_test <- predict(ridge_reg, s = optimal_lambda, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.567499

Elastic Net
```{r}
tibble::as_tibble(assessment_aggregate[train_ind,])
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
 rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+tax, 
 data = assessment_aggregate[train_ind,],
  method = "glmnet",
  trControl = cv_10
)
elastic_net

# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were alpha = 1 and lambda = 0.06549203.

elastic_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 1, family = 'gaussian', lambda =  0.06549203)
predictions_test <- predict(elastic_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.54861
